### 2023-03-05 paper/main.tex
updated files for the paper
formatting for title page and description of requirements for main body

\section{Problem Definition}
Develop a software that facilitates administration of surveys and feedback collection. The software must be fast, robust, and friendly.

@@

\section{Application Benefits}

\section{Requirements Elicitation and Specification}
Two types of users/roles: Feedback Gatherer / Respondent.

@@

\section{Top-level and Low-level Software Design}

\section{Software Construction}

\section{Technical Documentation}

\section{Acceptance Testing}

>>>>

\section{Problem Definition}
\subsection{outline the problem requirements and include the ap- plication domain and motivations of your project (1 page).}
Develop a software that facilitates administration of surveys and feedback collection. The software must be fast, robust, and friendly.

@@

\section{Application Benefits}
\subsection{what are the benefits of your application when compared to existing systems. Choose two systems only and include their references (2 pages).}

\section{Requirements Elicitation and Specification}
\subsection{Functional requirements list (only the ones that you have imple- mented) for each user role (two exactly). Name each requirement and explain it briefly.}
\subsection{For each user role, provide the use case diagram with all the use cases and actors.}
\subsection{Describe in detail two use cases using the activity diagram. Choose the most complex use cases.}
\subsection{Software qualities: Correctness, Time-eﬀiciency and Robustness. In- clude at least two concrete examples for each quality for each user role. The sign-in and sign-up use cases are excluded from the examples.
}

Two types of users/roles: Feedback Gatherer / Respondent.

@@

\section{Top-level and Low-level Software Design}
\subsection{Provide the MVC architecture according to the selected Web frame- work. Also, describe at least three benefits of MVC for your application.}
\subsection{Observer and Factory design patterns. Explain in detail the usability of these two patterns for your specific application. Include the complete class diagram for each pattern. Also provide the algorithms corresponding to the pattern’s important methods. For each class, provide the data types of the attributes and prototypes of the methods.}
\subsection{Provide the class diagram of the whole system by incorporating the two design patterns.
}

\section{Software Construction}
\subsection{Submit the screenshot of the entire structure of the code within the web framework.}
\subsection{Deployment diagram regarding the hardware configuration of the code. Indicate the supported Web browsers, the application/Web servers and the database solution.}
\subsection{Screenshots of all table contents of the system data.}
\subsection{GitHub link of the entire program. All students must contribute equally to the programming part. The commit log of each student will be checked within GitHub. Website builders, such as Wordpress, are not allowed.}
\subsection{Link of your Web-based application. The application should be acces- sible online and runnable.}

\section{Technical Documentation}
\subsection{List of programming languages.}
\subsection{List of reused algorithms and programs. Include their sources.}
\subsection{List of software tools and environments. Provide briefly their benefits specifically for your application.}

\section{Acceptance Testing: select test cases for both user roles. The sign-in and sign-up are excluded from testing.}
\subsection{Correctness testing using four test cases (screenshots of both inputs and out- puts).}
\subsection{Robustness testing using four test cases (screenshots of both inputs and out- puts).}
\subsection{Time-eﬀiciency testing of two functions (with screenshots). Indicate the method you used to measure the time.}
